Group B Analysis

### 2021-11-11 conference/CDS-abstract-figure.Rmd
added fig for E2

figA<-read_rds('../group-d/output/ETfig.rds')
figB<-read_rds('../group-d/output/ETfig.rds')
figC<-read_rds('../group-d/output/ETfig.rds')
figD<-read_rds('../group-d/output/ETfig.rds')
figE<-read_rds('../group-d/output/ETfig.rds')

@@

```{r}
A <- displayA + figA 
B <- displayA + figB 
C <- displayA + figC 
D <- displayD + figD 
E <- displayA + figE

@@

```{r}
ggsave('CDS-abstract-figure.pdf', scale = 1, width = 11, height = 7)

>>>>

figA<-read_rds('../group-d/output/ETfig.rds')
figB<-read_rds('../group-b/output/ETfig.rds')
figC<-read_rds('../group-d/output/ETfig.rds')
figD<-read_rds('../group-d/output/ETfig.rds')
figE<-read_rds('../group-d/output/ETfig.rds')

@@

```{r}
A <- displayA + figA 
B <- displayB + figB 
C <- displayC + figC 
D <- displayD + figD 
E <- displayE + figE

@@

```{r}
ggsave('CDS-abstract-figure.pdf', scale = 1, width = 12, height = 7)

### 2021-11-11 group-b/E2-analysis-replication.Rmd
adding expt example displays
added fig for E2

---
title: "Group B Analysis"
output: html_notebook
---

```{r message=FALSE}
library(jsonlite)
library(dplyr)
library(tidyr)
library(ggplot2)
library(ez)
```

# Import Data

Read JSON files and bind together into a tibble.

@@

# Extract relevant data

@@

Need to add condition information to the `task.data`

@@

# Question: Do people look more at the critical quadrant during free viewing?

Grab the relevant data, unnesting webgazer observations

@@

Add quadrant information to each observation

@@

Summarize proportion of views in each quadrant for each trial
```{r}
free.view.summary.trial.data <- free.view.data %>%
  group_by(subject_id, trial_index, relation) %>%
  summarize(critical = sum(normalized_quadrant == 'critical')/n(),
            first = sum(normalized_quadrant == 'first')/n(),
            second = sum(normalized_quadrant == 'second')/n(),
            third = sum(normalized_quadrant == 'third')/n()) %>%
  pivot_longer(c("critical", "first", "second", "third"), names_to = "normalized_quadrant", values_to = "proportion")
```
Summarize by subject
```{r}
free.view.summary.subject.data <- free.view.summary.trial.data %>%
  group_by(subject_id,relation,normalized_quadrant) %>%
  summarize(proportion = mean(proportion))
```

Summarize by condition 
```{r}
free.view.summary.condition.data <- free.view.summary.subject.data %>%
  group_by(normalized_quadrant, relation) %>%
  summarize(M = mean(proportion), SE = sd(proportion) / sqrt(n()))
```
```{r}
ggplot(free.view.summary.condition.data, aes(x=normalized_quadrant, y=M, ymax=M+SE, ymin=M-SE, fill=relation)) +
  geom_col(position=position_dodge())+
  geom_errorbar(position=position_dodge(width=0.9), width=0.1)+
  theme_classic()
```

>>>>

---
title: "Group B Analysis"
output: pdf
---

```{r message=FALSE}
library(jsonlite)
library(dplyr)
library(tidyr)
library(ggplot2)
#library(ez)
```

<!--Read JSON files and bind together into a tibble.-->

@@

<!--Extract relevant data-->

@@

<!-- add condition information to the `task.data`-->

@@

<!-- Question: Do people look more at the critical quadrant during free viewing?-->

<!--Grab the relevant data, unnesting webgazer observations-->

@@

<!--Add quadrant information to each observation-->

@@

<!--Summarize proportion of views in each quadrant for each trial-->
```{r}
free.view.summary.trial.data <- free.view.data %>%
  group_by(subject_id, trial_index, relation) %>%
  summarize(critical = sum(normalized_quadrant == 'critical')/n(),
            first = sum(normalized_quadrant == 'first')/n(),
            second = sum(normalized_quadrant == 'second')/n(),
            third = sum(normalized_quadrant == 'third')/n()) %>%
  pivot_longer(c("critical", "first", "second", "third"), names_to = "normalized_quadrant", values_to = "proportion")
```
<!--Summarize by subject-->
```{r}
free.view.summary.subject.data <- free.view.summary.trial.data %>%
  group_by(subject_id,relation,normalized_quadrant) %>%
  summarize(proportion = mean(proportion))
```

<!--Summarize by between condition -->
```{r}
free.view.summary.condition1.data <- free.view.summary.subject.data %>%
  group_by(normalized_quadrant) %>%
  summarize(M = mean(proportion), SE = sd(proportion) / sqrt(n()))
```

```{r}
fig<-ggplot(free.view.summary.condition1.data, aes(x=normalized_quadrant, y=M, ymax=M+SE, ymin=M-SE, fill = normalized_quadrant == "critical" )) +
  geom_col(position=position_dodge(), color = "black")+
  geom_errorbar(position=position_dodge(width=0.9), width=0.1)+
  scale_fill_brewer(palette="Set1",)+
  theme_classic()+
  labs(x = "Quadrant", y = "Mean proportion of looks")+
  theme(legend.position = "none")
fig
```
```{r, eval=FALSE}
saveRDS(fig, "output/ETfig.rds")

```

<!--Summarize by between and within conditions -->
```{r}
free.view.summary.condition.data <- free.view.summary.subject.data %>%
  group_by(normalized_quadrant, relation) %>%
  summarize(M = mean(proportion), SE = sd(proportion) / sqrt(n()))
```

```{r}
ggplot(free.view.summary.condition.data, aes(x=normalized_quadrant, y=M, ymax=M+SE, ymin=M-SE, fill=relation)) +
  geom_col(position=position_dodge(), color = "black")+
  geom_errorbar(position=position_dodge(width=0.9), width=0.1)+
  theme_classic()+
  labs(x = "Quadrant", y = "Mean proportion of looks")
```
